---
title: "Untitled"
author: "Jiaxuan"
date: "2/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message=F}
library(tidyverse)
library(broom)
```

```{r message=F}
score_transport <- read_csv("~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/score_transport.csv")
score_amenities <- read_csv("~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/score_amenities.csv")
score_greenery <- read_csv("~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/score_greenery.csv")
score_safety <- read_csv("~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/score_safety.csv")
score_noise <- read_csv("~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/score_noise.csv")
```

# Use Spearman's correlation, as density is not always in normal distribution
```{r}
#shapiro.test(df_greenery$density_km)
```

``{r message=F}
popn <- read_csv("/Users/jiaxuan/Library/CloudStorage/OneDrive-NationalUniversityofSingapore/MUP_year2/dissertation/datasets/nyc/nyc-residents-by-subzone-and-type-of-dwelling-2011-2019/planning-area-subzone-age-group-sex-and-type-of-dwelling-june-2011-2019.csv")

popn$subzone <- toupper(popn$subzone)
``


``{r}
popn_subzone <- popn %>%
  filter(year == 2019) %>%
  group_by(subzone) %>%
  summarise(population = sum(resident_count)) %>%
  filter(subzone %in% score_transport$ntaname) %>%
  arrange(subzone)

c1 <- popn_subzone$population
``

``{r}
df_transport <- left_join(score_transport, popn_subzone, by = c("ntaname" = "subzone"))

cor.test(df_transport$avg_score, df_transport$population)
``
# transport
```{r message=F}
bus <- read_csv("/Users/jiaxuan/Library/CloudStorage/OneDrive-NationalUniversityofSingapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/bus_stop_density.csv")
```

``{r}
bus <- bus %>%
  group_by(ntaname) %>%
  summarise(density = max(density))
``

```{r}
df_transport <- left_join(score_transport, bus, by = "ntaname")
cor.test(df_transport$avg_score, df_transport$density, method = "spearman") #, exact=FALSE
```

# greenery
```{r message=F}
tree <- read_csv("/Users/jiaxuan/Library/CloudStorage/OneDrive-NationalUniversityofSingapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/tree_density.csv")
```

``{r}
tree <- tree %>%
  group_by(ntaname) %>%
  summarise(density = max(density))
``

```{r}
df_greenery <- left_join(score_greenery, tree, by = "ntaname")
cor.test(df_greenery$avg_score, df_greenery$density, method = "spearman") #, exact=FALSE
```

# amenities
```{r message=F}
poi <- read_csv("/Users/jiaxuan/Library/CloudStorage/OneDrive-NationalUniversityofSingapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/poi_density.csv")
```

``{r}
poi <- poi %>%
  group_by(ntaname) %>%
  summarise(density = max(density))
``

```{r}
df_amenities <- left_join(score_amenities, poi, by = "ntaname")
cor.test(df_amenities$avg_score, df_amenities$density, method = "spearman")
```


# safety
```{r message=F}
crime <- read_csv("/Users/jiaxuan/Library/CloudStorage/OneDrive-NationalUniversityofSingapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/crime_nta.csv")
```

```{r}
df_safety <- left_join(score_safety, crime, by = "ntaname")
cor.test(df_safety$avg_score, df_safety$crime_rate, method = "spearman")
```


# noise
```{r message=F}
laeq <- read_csv("/Users/jiaxuan/Library/CloudStorage/OneDrive-NationalUniversityofSingapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/laeq_75.csv")
```

```{r}
laeq <- laeq %>%
  group_by(NAME) %>%
  summarise(HECTARES = sum(HECTARES),
            cov_area = sum(cov_area))

laeq$coverage <- laeq$cov_area/(laeq$HECTARES*10000)
```

```{r}
df_noise <- left_join(score_noise, laeq, by = "NAME")
cor.test(df_noise$avg_score, df_noise$coverage, method = "spearman")
```

