---
title: "Untitled"
author: "Jiaxuan"
date: "2/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=F}
library(tidyverse)
library(skimr)
```

# load datasets
```{r message=F}
transport <- read_csv("~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/transport.csv")
safety <- read_csv("~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/safety.csv")
noise <- read_csv("~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/noise.csv")
greenery <- read_csv("~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/greenery.csv")
amenities <- read_csv("~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/amenities.csv")
```

```{r}
my_skim <- skim_with(base = 
                       sfl(obs = length, iqr = IQR),
                       numeric = sfl(hist = NULL, p0 = NULL, p25 = NULL,
                                     p50 = NULL, p75 = NULL, p100 = NULL)
                    )
```

```{r}
#summary_transport <- transport %>% 
 # group_by(ntaname) %>% 
  #my_skim(overall_sentiment)

#write_delim(summary_transport, "/Users/jiaxuan/Desktop/1.txt", delim = " ")
```



# exclude those with obs.<3
```{r}
# transport
temp <- transport %>% 
  group_by(ntaname) %>% 
  summarise(obs = n()) %>%
  filter(obs>=3)

transport <- transport %>% filter(ntaname %in% temp$ntaname)

# amenities
temp <- amenities %>% 
  group_by(ntaname) %>% 
  summarise(obs = n()) %>%
  filter(obs>=3)

amenities <- amenities %>% filter(ntaname %in% temp$ntaname)

# greenery
temp <- greenery %>% 
  group_by(ntaname) %>% 
  summarise(obs = n()) %>%
  filter(obs>=3)

greenery <- greenery %>% filter(ntaname %in% temp$ntaname)

# safety
temp <- safety %>% 
  group_by(ntaname) %>% 
  summarise(obs = n()) %>%
  filter(obs>=3)

safety <- safety %>% filter(ntaname %in% temp$ntaname)

#noise
temp <- noise %>% 
  group_by(ntaname) %>% 
  summarise(obs = n()) %>%
  filter(obs>=3)

noise <- noise %>% filter(ntaname %in% temp$ntaname)
```


# group data and calculate avg
```{r}
score_transport <- transport %>%
  group_by(ntaname) %>%
  summarise(avg_score = mean(overall_sentiment),
            obs = n())

score_amenities <- amenities %>%
  group_by(ntaname) %>%
  summarise(avg_score = mean(overall_sentiment),
            obs = n())

score_greenery <- greenery %>%
  group_by(ntaname) %>%
  summarise(avg_score = mean(overall_sentiment),
            obs = n())

score_safety <- safety %>%
  group_by(ntaname) %>%
  summarise(avg_score = mean(overall_sentiment),
            obs = n())

score_noise <- noise %>%
  group_by(ntaname) %>%
  summarise(avg_score = mean(overall_sentiment),
            obs = n())
```

``{r}
names(safety)[names(safety) == "Sentence I"] <- "Sentence ID"
names(safety)[names(safety) == "reviewer_i"] <- "reviewer_id"
names(safety)[names(safety) == "reviewer_n"] <- "reviewer_name"
names(safety)[names(safety) == "aspect_pai"] <- "aspect_pair"
names(safety)[names(safety) == "descriptio"] <- "description"
names(safety)[names(safety) == "overall_se"] <- "overall_sentiment"
names(safety)[names(safety) == "overall_su"] <- "overall_subjectivity"
names(safety)[names(safety) == "des_polari"] <- "des_polarity"
names(safety)[names(safety) == "des_subjec"] <- "des_subjectivity"
``


```{r}
write_csv(score_transport, "~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/score_transport.csv")

write_csv(score_amenities, "~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/score_amenities.csv")

write_csv(score_greenery, "~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/score_greenery.csv")

write_csv(score_safety, "~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/score_safety.csv")

write_csv(score_noise, "~/OneDrive - National University of Singapore/MUP_year2/dissertation/datasets/nyc/qgis/csv_output/2/score_noise.csv")
```



